Solutions to Integer Programming from Quantum Annealing

### 2020-09-13 paper/main.tex
fixed all captions

\begin{figure*}
	\centering
	\begin{tabular}{p{0.2\textwidth}p{0.1\textwidth}p{0.2\textwidth}p{0.1\textwidth}p{0.2\textwidth}}
	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds0.pdf}
&&
	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds1.pdf}
&&
	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds2.pdf}\\
	\centering\bf{a} && \centering\bf{b} && \centering\bf{c}
	\end{tabular}
	\caption{Example of different dominating sets for $G(V, E)$. Vertices in the dominating set $D$ are highlighted in blue. {\bf{a)}} A dominating set of $G$ with domination number $\overline{\overline{D}} = 2$. {\bf{b)}} A minimal dominating set of $G$ with domination number of $\overline{\overline{D}} = 2$. {\bf{c)}} The minimum dominating set of $G$ with domination number of $\overline{\overline{D}} = 1$.}
	\label{fig:dominating_sets}
\end{figure*}

@@

In this paper, we propose an algorithm that maps ILP problems to QUBO.
This is achieved by the introduction of slack variables $s$ which turn the inequalities eq.~\eqref{eq:ilp-constraints} to equalities
\begin{align}
  \label{eq:ilp:slack}
  & \sum_i A_{a i}x_i + s_a + b_a = 0, \\
  & x_i, s_a \in \mathbb{Z} \geq 0.
\end{align}
While the coefficients of the inequality constraints are not required to be integer valued, the inequalities can be trivially rescaled such that $s_i \in \mathbbm{Z}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
Furthermore, this formalism can be generalized to constrained quadratic optimizations \ref{sec:methods:ilp:quadratic}.

We further improve the quantum annealer's performance by utilizing annealing offsets, which effectively delays the annealing schedule on a per-qubit basis. \cite{PhysRevA.96.042322,hsu2018quantum,10.1007/978-3-030-14082-3_14}
Converting to the Ising representation of the the problem Hamiltonian,
\begin{equation}
    \label{eq:HIsing}
     H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i ,
\end{equation}
we can recognize that Eq.~(\ref{eq:HIsing}) exhibits spin-glass properties. More specifically, if the $h_i$ coefficients are randomly drawn from a Bernoulli distribution, one expects spin-localization behavior to influence the outcome of the anneal.
In the case of quantum annealing, when an algorithm is mapped to its Ising representation, the values of $h_i$ will frequently take on various values, mimicking spin-glass like behavior.
More explicitly, the spin-glass enters a glassy state when more disorder is introduced ($|h_i|$ becomes large), and as a consequence, the wavefunction experiences Many-Body Localization (MBL) effects, the many-body analog of Anderson Localization~\cite{doi:10.1146/annurev-conmatphys-031214-014726,PhysRevE.90.022103,RevModPhys.91.021001}.
dd

@@

%----------------------------------------------------------------------------------------
\subsection{ILP QUBO}
\label{sec:results:qa1}
%----------------------------------------------------------------------------------------
Following Eq.~(\ref{eq:ilp:slack}), the ILP problems simplifies to solving a system of linear equations on integer valued variables. We map the integer variables $\vec z = \vec x, \vec s$ appearing in eq.~\eqref{eq:ilp:slack} to qubits under the following transformation~\cite{Chang:2018uoc}
\begin{align}
 z_i = & \sum_{r=0}^{R_i-1} 2^r \psi_{ri}
 \label{eq:int_to_bin}
\end{align}
where $\psi_{ri} \in \{0, 1\}$. The number of qubits used to represent the $i$-th integer variable is allowed to vary with $R_i$.
The integer-vector qubit transformation can be expressed as a rectangular matrix.
For example, a vector of two integer variables $z_0$ and $z_1$ represented by one and two qubits respectively is given as
\begin{align}
 \begin{pmatrix}
  z_0 \\
  z_1
 \end{pmatrix}
 = &
 \begin{pmatrix}
  2^0 & 0   & 0   \\
  0   & 2^0 & 2^1
 \end{pmatrix}
 \begin{pmatrix}
  \psi_{00} \\
  \psi_{01} \\
  \psi_{11}
 \end{pmatrix}
 \equiv T^z \begin{pmatrix}
  \psi_{00} \\
  \psi_{01} \\
  \psi_{11}
 \end{pmatrix}
\end{align}
If all variables are represented by the same number of qubits--$R_i$ is a constant for all $i$--then one can express the transformation as tensor product of bit vectors
\begin{align}
 \mathcal{R} =  & \begin{pmatrix} 2^0 & \dots & 2^{R-1}\end{pmatrix},    \\
 \mathcal{Z} =  & \begin{pmatrix} z_0 & \dots & z_{N-1}\end{pmatrix},    \\
 |\mathds{1}| = & |\mathcal{Z}|,                 \\
 T^z =          & \mathds{1}\otimes \mathcal{R}.
\end{align}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{./new_figures/DWave_scaling.pdf}
	\caption{Baseline result of DWave (black) compared to random guessing (blue). The jagged nature of random guessing reflects the degeneracy of the ground state. The legend labels the values of annealing offsets employed. A positive offsets (yellow) indicates that qubits with large values of $|h_i|$ are annealing with a delayed schedule, while negative offsets (green) delay the schedule of qubits with small values of $h_i$.}
	\label{fig:baseline}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{./new_figures/NN2_offset_scaling.pdf}
	\caption{The probability of finding the MDS for $G(2)$ from DWave (orange) and results from simulation with both decoherence terms (blue).
     The machine parameters are identical to Sec.~\ref{sec:discussion:qa} with the exception of shortening the total annealing time to 1 $\mu s$ to accommodate reasonable simulation times.}
	\label{fig:dwave1us}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{./new_figures/final_state_distribution.pdf}
	\caption{{\color{red}I need to add dwave final state distribution here too.}}
	\label{fig:final_state_distribution}
\end{figure}

@@

%========================================================================================
\section{METHODS}
\label{sec:methods}
%========================================================================================
%----------------------------------------------------------------------------------------
\subsection{Additional Mappings to QUBO}
\label{sec:methods:ILP-to-QUBO}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\subsubsection{Minimum Dominating Set Qubo}
\label{sec:methods:mds-qubo}
%----------------------------------------------------------------------------------------

@@

The target QUBO in the notation of eq.~\eqref{eq:matrix_form} reads
 {\small
  \begin{align}
   Q_{xx} & = \mathbbm{1} + p\left[J^T J + J^T + J - 2 \mathrm{diag}(|J|) - \mathbbm{1} \right] \,, \\
   Q_{sx} & = - p(\mathbbm{1}+J^T)T_s\,,                                                                     \\
   Q_{ss} & = p\left[{T_s}^T T_s + 2\mathrm{diag}(|T_s|)\right]\,,                                  \\
   C      & =  p \overline{\overline{V}}\,,
  \end{align}}
where $ |M| \equiv \sum_{\nu} M_{\nu \mu}$.

@@

In this case the $Q_{xx}$ component of the Qubo, eq.~\eqref{eq:qubo:components} obtains a new term
\begin{equation}
    Q_{xx} \to Q_{xx} + T_x^T d T_x \, .
\end{equation}

@@

The minimal energy solution to eq.~\eqref{eq:initial-ip-def} and eq.~\eqref{eq:qubo-min} {\color{red}@chris what equation is this?} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
Thus some knowledge of the problem is required.
In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large $p$-values increase the highest available energy of the system by multiples of $p$.
After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
Thus, if solvers have finite precision, one must estimate reasonable values for $p$: for large $p$ more solutions fulfill the constraints, while for small $p$, more solutions minimize the objective function.

@@

To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
\begin{align}
 \partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
\end{align}
where $\rho (t)$ is the density matrix at time $t$.
$H(t)$ is the time-dependent Hamiltonian
\begin{align}
 \label{eq:annealH}
 H_{anneal}(t) & =  - \sum_i  A_i(t)\sigma^x_i                                                                      & \notag \\
 +             & \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i  , &
\end{align}
where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions.
The site dependency takes into account of the annealing offset.
$[,]$ denotes the Lie bracket.
$L_j$ are the Lindblad operators for decoherence.
$\{, \}$ denotes the anti-commutator.

We consider two types of decoherence models: full counting statistics \cite{PhysRevE.90.022103} and local damping.
The full counting statistics term models the global decoherence to all the qubits due to the classical reservoir.
The local damping term models the decoherence of each qubit independently.
For full counting statistics, the Lindblad operator is
\begin{align}
\mathcal{L}[\rho (t)] &=& \Gamma_{fc} \sum_j   (2 S_j \rho(t) S_j^\dagger - \{ S^\dagger_j S_j, \rho(t) \}) \notag \\
&& + e^{-\beta \Delta E_j} (2 S_j^\dagger \rho(t) S_j - \{ S_j S^\dagger_j, \rho(t) \} )
\end{align}
where $j$ is the index for the inter-level spacing $\Delta E_j=E_\mu-E_\nu>0$. $S_j=|E_\nu \rangle \langle E_\mu|$ denotes the many-body lowering operator.
$\{, \}$ denotes the anti-commutator. $\Gamma = 1/T_c$ is the decoherence rate for coherence time $T_c$.
That is, due to the interaction with the classical thermal bath, there is a probability that the system hops from each higher-energy many-body state to a lower-energy many-body state.
The probability of the inverse process is given by a Boltzmann factor.
To model the local decoherence of each qubits in the non-interacting limit, we also consider the amplitude damping for non-interacting qubits.
The Lindblad operator is
\begin{align}
\mathcal{L}[\rho (t)] &=&  \Gamma_{loc} \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \} \notag \\
&& + e^{-\beta 2|h_j| }  (2L_j^\dagger \rho(t) L_j - \{ L_j L_j^\dagger, \rho(t) \}) ),
\end{align}
where $j$ is the index for qubit.
$L_j= \sigma^{+}_j=|1\rangle \langle 0|$ for $h_j>0$ and $L_j= \sigma^{-}_j=|0\rangle \langle 1|$ for $h_j<0$.
That is, each qubit is damped toward its local ground state if we ignore all the interactions.

The initial condition is the Gibbs canonical ensemble
\begin{equation}
\rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}[e^{-\beta H(0)}]} ,
\end{equation}
where $\beta$ is the inverse temperature.
The probability to get the ground state at measurement is
\begin{align}
P =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
\end{align}
where the projection operator onto the degenerated ground states subspace is defined as $\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $.
Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.

@@

\begin{figure}[htb]
 \centering
  \includegraphics[width=\columnwidth]{./new_figures/anneal_schedule.pdf}
  \caption{
  Anneal schedules for amplitudes of initial Hamiltonian (top left to bottom right) and final Hamiltonian (bottom left to top right) are displayed for a complete anneal schedule.
  Different colors represent different offesets: delayed (light to dark), default (black).
 }
 \label{fig:anneal_schedule}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{./new_figures/anneal_schedule_extended.pdf}
	\includegraphics[width=\columnwidth]{./new_figures/NN2_offset_scaling_extended.pdf}
	\caption{{\color{red}I need to add dwave final state distribution here too.}}
	\label{fig:anneal_schedule_ext}
\end{figure}

@@

It unfortunately does not make much sense to remove all decoherence models for the $G(2)$ graph for an anneal time of $1\mu s$ since all probabilities go to 1 within machine precision.

%----------------------------------------------------------------------------------------
\subsubsection{Other Simulation Details}
\label{sec:methods:simulation_details}
%----------------------------------------------------------------------------------------
To check the correctness of simulator and unit conversion, we tested a simple annealing schedule for pure transverse field, i.e. $A(s)=A(0)$ and $B(s)=0$.
The initial state is pure zero state $\rho=|00...0\rangle \langle 00...0|$.
In this case the analytical solution can be obtained for the wave function oscillation.
The time-dependent probability is $P_{0}=\cos^{2n}(s)=\cos^{2n}(t/T)$ where $n$ is the number of qubits and $T$ is the annealing time.
For annealing time $T=1/A(0)$, we expect to see perfect one-period oscillation. The energy spectrum for this system can be analytically obtained, so we also checked the Boltzmann distribution in the initial density matrix construction. The oscillation is depicted in Figure \ref{figcheck}, where the simulation matches the expected theoretical behavior.

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{./new_figures/time_dependent_probability.pdf}
	\caption{(Left) The time-dependent probability of resolving the ground state and (Right) the corresponding mutual information. (Top) Simulation with decoherence included and (Bottom) without decoherence.}
	\label{fig:td_prob}
\end{figure}

>>>>

\begin{figure*}
	\centering
	\begin{tabular}{p{0.2\textwidth}p{0.1\textwidth}p{0.2\textwidth}p{0.1\textwidth}p{0.2\textwidth}}
	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds0.pdf}
&&
	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds1.pdf}
&&
	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds2.pdf}\\
	\centering\textbf{a} && \centering\textbf{b} && \centering\textbf{c}
	\end{tabular}
	\caption{Example of different dominating sets for $G(V, E)$. Vertices in the dominating set $D$ are highlighted in blue. {\textbf{a)}} A dominating set of $G$ with domination number $\overline{\overline{D}} = 2$. {\textbf{b)}} A minimal dominating set of $G$ with domination number of $\overline{\overline{D}} = 2$. {\textbf{c)}} The minimum dominating set of $G$ with domination number of $\overline{\overline{D}} = 1$.}
	\label{fig:dominating_sets}
\end{figure*}

@@

In this paper, we propose an algorithm that maps ILP problems to QUBO.
This is achieved by the introduction of slack variables $s$ which turn the inequalities Eq.~\eqref{eq:ilp-constraints} to equalities
\begin{align}
  \label{eq:ilp:slack}
  & \sum_i A_{a i}x_i + s_a + b_a = 0, \\
  & x_i, s_a \in \mathbb{Z} \geq 0.
\end{align}
While the coefficients of the inequality constraints are not required to be integer valued, the inequalities can be trivially rescaled such that $s_i \in \mathbbm{Z}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
Furthermore, this formalism can be generalized to constrained quadratic optimizations \ref{sec:methods:ilp:quadratic}.

We further improve the quantum annealer's performance by utilizing annealing offsets, which effectively delays the annealing schedule on a per-qubit basis~\cite{PhysRevA.96.042322,hsu2018quantum,10.1007/978-3-030-14082-3_14}.
Converting to the Ising representation of the the problem Hamiltonian,
\begin{equation}
    \label{eq:HIsing}
     H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i ,
\end{equation}
we can recognize that Eq.~(\ref{eq:HIsing}) exhibits spin-glass properties. More specifically, if the $h_i$ coefficients are randomly drawn from a Bernoulli distribution, one expects spin-localization behavior to influence the outcome of the anneal.
In the case of quantum annealing, when an algorithm is mapped to its Ising representation, the values of $h_i$ will frequently take on various values, mimicking spin-glass like behavior.
More explicitly, the spin-glass enters a glassy state when more disorder is introduced ($|h_i|$ becomes large), and as a consequence, the wavefunction experiences Many-Body Localization (MBL) effects, the many-body analog of Anderson Localization~\cite{doi:10.1146/annurev-conmatphys-031214-014726,PhysRevE.90.022103,RevModPhys.91.021001}.

@@

%----------------------------------------------------------------------------------------
\subsection{ILP QUBO}
\label{sec:results:qa1}
%----------------------------------------------------------------------------------------
Following Eq.~(\ref{eq:ilp:slack}), the ILP problems simplifies to solving a system of linear equations on integer valued variables. We map the integer variables $\vec z = \vec x, \vec s$ appearing in Eq.~\eqref{eq:ilp:slack} to qubits under the following transformation~\cite{Chang:2018uoc}
\begin{align}
 z_i = & \sum_{r=0}^{R_i-1} 2^r \psi_{ri}
 \label{eq:int_to_bin}
\end{align}
where $\psi_{ri} \in \{0, 1\}$. The number of qubits used to represent the $i$-th integer variable is allowed to vary with $R_i$.
The integer-vector qubit transformation can be expressed as a rectangular matrix.
For example, a vector of two integer variables $z_0$ and $z_1$ represented by one and two qubits respectively is given as
\begin{align}
 \begin{pmatrix}
  z_0 \\
  z_1
 \end{pmatrix}
 = &
 \begin{pmatrix}
  2^0 & 0   & 0   \\
  0   & 2^0 & 2^1
 \end{pmatrix}
 \begin{pmatrix}
  \psi_{00} \\
  \psi_{01} \\
  \psi_{11}
 \end{pmatrix}
 \equiv T^z \begin{pmatrix}
  \psi_{00} \\
  \psi_{01} \\
  \psi_{11}
 \end{pmatrix}
\end{align}
If all variables are represented by the same number of qubits--$R_i$ is a constant for all $i$--then one can express the transformation as tensor product of bit vectors
\begin{align}
 \mathcal{R} =  & \begin{pmatrix} 2^0 & \dots & 2^{R-1}\end{pmatrix},    \\
 \mathcal{Z} =  & \begin{pmatrix} z_0 & \dots & z_{N-1}\end{pmatrix},    \\
 |\mathds{1}| = & |\mathcal{Z}|,                 \\
 T^z =          & \mathds{1}\otimes \mathcal{R}.
\end{align}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{./new_figures/DWave_scaling.pdf}
	\caption{Baseline result of DWave (black) compared to random guessing (dashed green). The jagged nature of random guessing reflects the degeneracy of the ground state. Negative offsets with a `s' tag (blue) are results from delays of large values of $|h_i|$, while negative offsets with the `w' label (red) delay the schedule of qubits with small values of $h_i$.}
	\label{fig:baseline}
\end{figure}

@@

\begin{figure}[b]
	\centering
	\includegraphics[width=\columnwidth]{./new_figures/NN2_offset_scaling.pdf}
	\caption{The probability of finding the MDS for $G(2)$ from DWave (black) and simulation (dashed yellow) at annealing times of 1 $\mu s$.}
	\label{fig:dwave1us}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{./new_figures/final_state_distribution.pdf}
	\caption{Final state distribution from DWave (solid bars) and simulation (black outline). The colors label the type of offset  The $(0, 1, 0, 0, 0)$ state is the first solution where vertex 1 is in the dominating set. The $(1, 0, 0, 1, 0)$ state is the second solution where vertex 0 is in the dominating set. The first excited state is the $(1, 1, 1, 1, 1)$ state where both vertices are in the dominating set.}
	\label{fig:final_state_distribution}
\end{figure}

@@

%========================================================================================
\section{METHODS}
\label{sec:methods}
%========================================================================================
%----------------------------------------------------------------------------------------
\subsection{Additional Mappings to QUBO}
\label{sec:methods:ILP-to-QUBO}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\subsubsection{Minimum Dominating Set QUBO}
\label{sec:methods:mds-qubo}
%----------------------------------------------------------------------------------------

@@

The target QUBO in the notation of Eq.~\eqref{eq:matrix_form} reads
 {\small
  \begin{align}
   Q_{xx} & = \mathbbm{1} + p\left[J^T J + J^T + J - 2 \mathrm{diag}(|J|) - \mathbbm{1} \right] \,, \\
   Q_{sx} & = - p(\mathbbm{1}+J^T)T_s\,,                                                                     \\
   Q_{ss} & = p\left[{T_s}^T T_s + 2\mathrm{diag}(|T_s|)\right]\,,                                  \\
   C      & =  p \overline{\overline{V}}\,,
  \end{align}}
where $ |M| \equiv \sum_{\nu} M_{\nu \mu}$.

@@

In this case the $Q_{xx}$ component of the QUBO, Eq.~\eqref{eq:qubo:components} obtains a new term
\begin{equation}
    Q_{xx} \to Q_{xx} + T_x^T d T_x \, .
\end{equation}

@@

The minimal energy solution to Eq.~\eqref{eq:initial-ip-def} and Eq.~\eqref{eq:qubo-min} {\color{red}@chris what equation is this?} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
Thus some knowledge of the problem is required.
In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large values of For$p$ increase the highest available energy of the system by multiples of $p$.
After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
Thus, if solvers have finite precision, one must estimate reasonable values for $p$: for large $p$ more solutions fulfill the constraints, while for small $p$, more solutions minimize the objective function.

@@

To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we evaluate the master equation in Lindblad form
\begin{align}
 \partial_t \rho (t) = &  \frac{-i}{\hbar} \left[H(t) , \rho(t)\right] \nonumber \\
 & + \sum_j \left(2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}\right) ,
\end{align}
where $\rho (t)$ is the density matrix at time $t$.
$H(t)$ is the time-dependent Hamiltonian
\begin{align}
 \label{eq:annealH}
 H_{anneal}(t)  = & - \sum_i  A_i(t)\sigma^x_i +\sum_i B_{i}(t) h_i \sigma^z_i \notag \\
 & + \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j  ,
\end{align}
where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions.
The site dependency takes into account of the annealing offset.
$[,]$ denotes the Lie bracket.
$L_j$ are the Lindblad operators for decoherence.
$\{, \}$ denotes the anti-commutator.

We consider two types of decoherence models: full counting statistics \cite{PhysRevE.90.022103} and local damping.
The full counting statistics term models the global decoherence to all the qubits due to the classical reservoir.
The local damping term models the decoherence of each qubit independently.
For full counting statistics, the Lindblad operator is
\begin{align}
\mathcal{L}[\rho (t)] = & \Gamma_{\textrm{fc}} \sum_j   \left(2 S_j \rho(t) S_j^\dagger - \{ S^\dagger_j S_j, \rho(t) \}\right) \notag \\
& + e^{-\beta \Delta E_j} \left(2 S_j^\dagger \rho(t) S_j - \{ S_j S^\dagger_j, \rho(t) \} \right)
\end{align}
where $j$ is the index for the inter-level spacing $\Delta E_j=E_\mu-E_\nu>0$. $S_j=|E_\nu \rangle \langle E_\mu|$ denotes the many-body lowering operator.
$\{, \}$ denotes the anti-commutator. $\Gamma = 1/T_c$ is the decoherence rate for coherence time $T_c$.
That is, due to the interaction with the classical thermal bath, there is a probability that the system hops from each higher-energy many-body state to a lower-energy many-body state.
The probability of the inverse process is given by a Boltzmann factor.
To model the local decoherence of each qubits in the non-interacting limit, we also consider the amplitude damping for non-interacting qubits.
The Lindblad operator is
\begin{align}
\mathcal{L}[\rho (t)] = &  \Gamma_{\textrm{loc}} \sum_j \left(2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \} \right)\notag \\
& + e^{- 2 \beta |h_j| }  \left(2L_j^\dagger \rho(t) L_j - \{ L_j L_j^\dagger, \rho(t) \} \right) ,
\end{align}
where $j$ is the index for qubit.
$L_j= \sigma^{+}_j=|1\rangle \langle 0|$ for $h_j>0$ and $L_j= \sigma^{-}_j=|0\rangle \langle 1|$ for $h_j<0$.
That is, each qubit is damped toward its local ground state if we ignore all the interactions.

The initial condition is the Gibbs canonical ensemble
\begin{equation}
\rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}\left(e^{-\beta H(0)}\right)} ,
\end{equation}
where $\beta$ is the inverse temperature.
The probability to get the ground state at measurement is
\begin{align}
P =  \mbox{Tr} \left( \rho (t) \pi_{\mbox{gnd}} \right)  ,
\end{align}
where the projection operator onto the degenerated ground states subspace is defined as $\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $.
Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.

@@

\begin{figure}[htb]
 \centering
  \includegraphics[width=\columnwidth]{./new_figures/anneal_schedule.pdf}
  \caption{
  Anneal schedules for amplitudes of initial Hamiltonian (dashed) and final Hamiltonian (solid).
  Offset 0.0 (black) and -0.05 (purple) are displayed.
  Intermediate values lie between and are suppressed for clarity.
 }
 \label{fig:anneal_schedule}
\end{figure}

@@

\begin{figure*}
    \centering
	\begin{tabular}{p{0.5\textwidth}p{0.5\textwidth}}
	\includegraphics[width=0.5\textwidth]{./new_figures/anneal_schedule_extended.pdf}
    &
	\includegraphics[width=0.5\textwidth]{./new_figures/NN2_offset_scaling_extended.pdf}\\
	\centering \textbf{a} & \centering \textbf{b}
	\end{tabular}
	\centering
	\caption{Extended annealing schedule and simulation result. \textbf{a)} The annealing time is increased by 10\% at both the start and end, and the initial values of $A(s)$ and $B(s)$ at non-zero offset are also not extrapolated in comparison to Fig.~\ref{fig:anneal_schedule}. Therefore, the initial and final Hamiltonian are no longer suffer systematic error at non-zero offset. \textbf{b)} The default (dashed yellow) result is one presented in Fig.~\ref{fig:dwave1us}. Results from extended schedules are presented shown with solid lines with full-counting statistics and amplitude damping (red), only full counting-statistics (blue), and only amplitude damping (green).
    }
	\label{fig:anneal_schedule_ext}
\end{figure*}

@@

It unfortunately does not make much sense to remove all decoherence models for the $G(2)$ graph for an anneal time of $1\mu s$ since all probabilities go to unity.

%----------------------------------------------------------------------------------------
\subsubsection{Other Simulation Details}
\label{sec:methods:simulation_details}
%----------------------------------------------------------------------------------------
To check the correctness of simulator and unit conversion, we tested a simple annealing schedule for pure transverse field, i.e. $A(s)=A(0)$ and $B(s)=0$.
The initial state is pure zero state $\rho=|00...0\rangle \langle 00...0|$.
In this case the analytical solution can be obtained for the wave function oscillation.
The time-dependent probability is $P_{0}=\cos^{2n}(s)=\cos^{2n}(t/T)$ where $n$ is the number of qubits and $T$ is the annealing time.
For annealing time $T=1/A(0)$, we expect to see perfect one-period oscillation. The energy spectrum for this system can be analytically obtained, so we also checked the Boltzmann distribution in the initial density matrix construction. The oscillation is depicted in Fig.~\ref{figcheck}, where the simulation matches the expected theoretical behavior.

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{./new_figures/time_dependent_probability.pdf}
	\caption{Time-dependent probability for resolving the ground state for simulation results presented in Sec.~\ref{sec:results:simulation}. Different offsets are labeled in the same way as Fig.~\ref{fig:baseline}.}
	\label{fig:td_prob}
\end{figure}
